Think again?\\ Optimal mental simulation tracks problem difficulty

### 2015-01-26 manuscript.tex
Silly discussion

\TODO{summarize results showing that experimen 2 replicates Smith \& Vul (2014)}

We fit the model in two steps. First, we fit $\sigma_p$, $\kappa_v$, $\kappa_m$, $\kappa_b$, and $\sigma_0$ to particant's responses in Experiment 2. \TODO{explain the procedure by which we did this fitting} Using this procedure, we found the best fitting parameters to be $\sigma_p=31.02$, $\kappa_v=255.60$, $\kappa_m=502850.41$, $\kappa_b=50.42$, and $\sigma_0=167.06$.

@@

\section{Does SPRT explain human judgments?}

Participant responses were well correlated with the SPRT model ($r=0.81$, 95\% CI [0.77, 0.84]), and slightly less so with a SPRT model with $T=2$ ($r=0.78$, 95\% CI [0.74, 0.81]). There was also a significant correlation with resonse time for the $T=2$ SPRT model ($r=0.35$, 95\% CI [0.27, 0.43]). However, it turns out that the number of bounces is a much better predictor of people's response times than the model itself.

\TODO{figure}

\TODO{explain SPRT results}

@@

\TODO{}

>>>>

\section{Results}

We fit the model to people's responses in two steps. First, we fit $\sigma_p$, $\kappa_v$, $\kappa_m$, $\kappa_b$, and $\sigma_0$ to particant's responses in Experiment 2. \TODO{explain the procedure by which we did this fitting} Using this procedure, we found the best fitting parameters to be $\sigma_p=31.02$, $\kappa_v=255.60$, $\kappa_m=502850.41$, $\kappa_b=50.42$, and $\sigma_0=167.06$. With these parameters, we find very similar results to those from \citeA{Smith:2013fc} (Figure \TODO{}, left subplot). In particular, we found a correlation of $r=0.94$ \TODO{cis} between the model's predicted means of where the ball would end up and people's average location of the paddle.

@@

Participant responses were well correlated with a SPRT model with $T=1$ ($r=0.81$, 95\% CI [0.77, 0.84]), and slightly less so with a SPRT model with $T=2$ ($r=0.78$, 95\% CI [0.74, 0.81]). There was also a significant correlation with resonse time for the $T=2$ SPRT model as computed with Equation \ref{eq:rt} ($r=0.71$, \TODO{95\% CI []}). Figure \TODO{} shows human responses as a function of the model's responses for $T=2$ (middle subplot) as well as human response times as a function of the model's response times (right subplot).

@@

In this paper, we asked the question: how many simulations do people run? We hypothesized that although people probably take a very small number of samples \cite{Vul:2014ba}, people still vary the number of samples that they take in order to exploit the fact that some judgments are easier to make than others. Specifically, we hypothesized that people take samples in a manner consistent with the SPRT strategy, in which evidence for hypotheses is accumulated until one hypothesis has a fixed amount of evidence over the other.

The results of Experiment 1 paint a clear picture that people \emph{do} vary the number of samples they take, as evidenced by the increase in response time on ``hard'' trials (i.e., trials which people are less confident about). This pattern of taking longer to respond on trials with $p\approx 0.5$ is qualitatively consistent with the strategy of SPRT. To demonstrate quantitatively that SPRT is a good account for people's responses, we formulated a model of people's responses based on the ``Noisy Newton'' hypothesis and SPRT. In Experiment 2, replicated the experiment from \citeA{Smith:2013fc}, and used the results to fit our model. Comparing people's responses and response times in Experiment 1 to those of the model, we found an extremely strong fit, suggesting that people are relying both on simulations from approximate physical simulations, and that they vary the number of simulations that they run according to SPRT.
